PANCHANGE_data_preprocessing

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
Made comments to retro and baseline comparison chunk
Update PANCHANGE_data_preprocessing2020-07-15.Rmd

This will is the preprocessing script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)

@@

```{r pre, base, retro comparison for phq, pcl and gad}

>>>>

This is the preprocessing script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)

@@

```{r pre, base, retro comparison for phq, pcl and gad}
#see Issue for more details here
```
